Gaia DR2 view of the GD-1 stellar stream

### 2018-04-27 paper/gd1.tex
abstract

\begin{abstract}\noindent % trust me
Tidally-disrupted globular clusters leave behind thin, dynamically-cold streams
of stars that are extremely valuable tracers of the large- and small-scale
properties of mass around the Galaxy.
Many thin stellar streams have been discovered around the Milky Way, the
majority of which exist in the Galactic halo and are therefore primarily
sensitive to the distribution of dark matter.
Here we present astrometric data for one of the longest stellar streams --- the
``GD-1'' stream --- from data release 2 (\DR) of the \gaia\ mission.
We re-discover significant density variations along the stream by selecting
candidate member stars using the exquisite \gaia\ data alone, including the
existence of a prominent, apparent gap in the stream.
<Using photometric data from the \pans, we refine our selection ...>
These density variations --- and especially the gap --- are possible indications
of past interactions with large, massive perturbers.
<estimate the mass of interaction...>
\end{abstract}

@@

Dynamically cold stellar streams, likely formed from the tidal disruption of globular clusters, are sensitive to the large and small scale distribution of matter in the halo

Thin stellar streams form from the tidal disruption of low-dispersion stellar systems such as globular clusters \citep[e.g.,][]{TODO}. To date, $\approx$13--14 thin streams have been discovered by searching large-area sky surveys such as the Sloan Digital Sky Survey (SDSS) and Pan-STARRS1 survey (PS1). These previously known thin streams span a wide range of lengths \citep[$\sim$$2$--$60$ deg;][]{bernard14,grillmair06} and masses \citep[$\sim$$10^3$--$10^5~\msun$;][]{TODO,TODO}, however, only two such streams have clear progenitor systems: NGC 5466 and Palomar 5 \citep{TODO,TODO}. Though it has been shown with many independent methods that modeling these thin streams can place strong constraints on the gravitational potential in which they form \citep{apw14,TODO}, many efforts to apply these models to real streams around the Milky Way have been hampered by the small number of known progenitor systems.

@@

>>>>

\begin{abstract}\noindent % trust me
Tidally-disrupted globular clusters leave behind thin, dynamically-cold streams
of stars that are extremely valuable tracers of the large- and small-scale
properties of mass around the Galaxy.
Many thin stellar streams have been discovered around the Milky Way, the
majority of which exist in the Galactic halo and are therefore primarily
sensitive to the distribution of dark matter.
Here we present astrometric data for one of the longest stellar streams --- the
``GD-1'' stream --- from data release 2 (\DR) of the \gaia\ mission.
We re-discover significant density variations along the stream by selecting
candidate member stars first using only the exquisite \gaia\ data.
Combined with filtering using Pan-STARRS photometry, we see clear evidence of
multiple prominent under-densities and haps in the stream.
These density variations --- and especially the gaps --- are possible
indications of past interactions with large, massive perturbers.
Given that the orbit of the stream crosses the Milky Way disk at large radius,
these perturbers are likely halo objects and have masses consistent with XX,
suggestive of dark matter sub-halos.
\end{abstract}

@@

Dynamically cold stellar streams, likely formed from the tidal disruption of
globular clusters, have been discovered throughout the Milky Way halo (e.g.,
\citealt{TODO}).

To date, $\approx$13--14 thin streams have been discovered by searching large-area sky surveys such as the Sloan Digital Sky Survey (SDSS) and Pan-STARRS1 survey (PS1). These previously known thin streams span a wide range of lengths \citep[$\sim$$2$--$60$ deg;][]{bernard14,grillmair06} and masses \citep[$\sim$$10^3$--$10^5~\msun$;][]{TODO,TODO}, however, only two such streams have clear progenitor systems: NGC 5466 and Palomar 5 \citep{TODO,TODO}. Though it has been shown with many independent methods that modeling these thin streams can place strong constraints on the gravitational potential in which they form \citep{apw14,TODO}, many efforts to apply these models to real streams around the Milky Way have been hampered by the small number of known progenitor systems.

@@

- Transform to GD-1 coordinates (Koposov et al.)
    - Can see deviation from great circle
- Cut to be close to latitude = 0
- Cut to get proper motion over-density
- Color-magnitude filtering

Figure 1:
- PM cut (panel a)
- PM + CMD cut (panel b)
- SFD (panel c)??

Comment on these here - add figure for both in Appendix?
- Dust / no significant extinction - combine with other figure
- Scanning pattern - just discuss, no figure
